---
title: "5513assignment 1"
author: "Tiansi Zhu"
format:
    html: default
    pdf: default
subtitle: "student id:35742305"
editor: 
  markdown: 
    wrap: sentence
---

### Introduction

This report examines the relationship between marketing spending and customer purchases.I want to find out if higher marketing expenditure leads to more customer spending.This data comes from a personalized marketing campaign in the past quarter.The analysis will help businesses create more effective marketing strategies.

### Research Question

The core research question of this report is: Does higher marketing spend lead to higher purchase amount for customers? I will analyze the correlation between marketing investment and customer spending behavior using this dataset.I will also further examine whether there are differences in marketing effectiveness across different customer segments.

```{r}
#| echo: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE )
```

### Dataset Introduction

This dataset comes from the personalized marketing records of an online retailer, with 150 customer samples.It covers key fields like customer ID, signup date, marketing spend, visits, purchase amount, and customer segment.Missing values in the purchase amount variable were removed during data cleaning.The cleaned dataset is neat and complete, which is enough for us to analyze the relationship between marketing investment and consumption performance.

```{r}
library(tidyverse)
library(here)
data1 <- read_csv(here::here("data", "35742305_Tiansi Zhu.csv")) 
data <- data1 %>% 
 filter(!is.na(data1$purchase_amount))
dim(data)
names(data)
str(data)
```