---
title: "5513assignment 1"
author: "Tiansi Zhu"
format:
    html: default
    pdf: default
subtitle: "student id:35742305"
editor: 
  markdown: 
    wrap: sentence
---

### Introduction

This report examines the relationship between marketing spending and customer purchases.I want to find out if higher marketing expenditure leads to more customer spending.This data comes from a personalized marketing campaign in the past quarter.The analysis will help businesses create more effective marketing strategies.

### Research Question

The core research question of this report is: Does higher marketing spend lead to higher purchase amount for customers? I will analyze the correlation between marketing investment and customer spending behavior using this dataset.I will also further examine whether there are differences in marketing effectiveness across different customer segments.

```{r}
#| echo: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE )
```

### Dataset Introduction

This dataset comes from the personalized marketing records of an online retailer, with 150 customer samples.It covers key fields like customer ID, signup date, marketing spend, visits, purchase amount, and customer segment.Missing values in the purchase amount variable were removed during data cleaning.The cleaned dataset is neat and complete, which is enough for us to analyze the relationship between marketing investment and consumption performance.

```{r}
library(tidyverse)
library(here)
data1 <- read_csv(here::here("data", "35742305_Tiansi Zhu.csv")) 
data <- data1 %>% 
 filter(!is.na(data1$purchase_amount))
dim(data)
names(data)
str(data)
```
The data contains `r nrow(data)` rows and `r ncol(data)` columns. And it contains `r names(data)` 7 variables. The cleaned dataset retains `r nrow(data)` valid observations with complete variable counts, which can be directly used for subsequent statistical analysis and data visualization. All variables have undergone data type verification and missing value cleaning. Specifically, marketing_spend (marketing expenditure) and purchase_amount (purchase amount) are numerical variables, while segment (customer segment) is a character variable.

```{r}
ggplot(data, aes(x = marketing_spend)) +
  geom_histogram(binwidth = 20, fill = "steelblue", colour = "white") +
  labs(title = "Distribution of marketing spend",
       x = "marketing spend", y = "Count")
ggplot(data, aes(x = purchase_amount)) +
  geom_histogram(binwidth = 20, fill = "steelblue", colour = "white") +
  labs(title = "Distribution of purchase amount",
       x = "purchase amount", y = "Count")
```
Figure 1 shows the histogram of marketing spend, and Figure 2 shows the histogram of purchase amount. Both figures indicate that the values of the two variables are concentrated in the 0-200 range, with an overall right-skewed distribution. This suggests that most customers have moderate marketing investment and purchase amounts, while a small number of customers have high investment and consumption, providing a data background for the subsequent correlation analysis.
